Scattering Auditory Scenes for Classification: Supervised and Unsupervised Approaches

### 2016-06-27 paper/structureScene.tex
update section III

A recent improvement to the temporal scattering transform has been brought by \cite{Anden2015},

@@

\section{Feature design}
Before supervised or unsupervised classification, is it beneficial to process scattering coefficients with feature transformations that improve invariance, normality, or generalization power. 
This section reviews binaural data augmentation, feature selection, logarithmic compression, standardization, and temporal integration.
The former is novel and specific to stereophonic recordings, whereas the next ones would also apply to many other problems.

>>>>

This issue was remedied by time-frequency scattering \cite{Anden2015}, which performs a wavelet decomposition over the log-frequency variable $\gamma_1$ after the second-order wavelet decomposition over time.
While temporal scattering merely extracts the average amplitude modulation spectrum, time-frequency scattering computes spectral modulations at various temporal rates and spectral scales.
% link with GBFB and STRF which have proven useful for acoustic scene classification.

@@

\section{Feature design}
Before supervised or unsupervised classification, is it beneficial to process scattering coefficients with feature transformations that improve invariance, normality, or generalization power. 
This section reviews binaural data augmentation, feature selection, logarithmic compression, standardization, and temporal integration.
The former is novel and specific to stereophonic recordings, whereas the next ones would also apply to many other kinds of data.
